### 2019-08-09 ch0_frontmatter.tex
update manuscript
update texs and files

@@

	{\Huge \textsf{Studying dynamic processes\\with networks and trajectories}}

@@

\newpage{\thispagestyle{empty}\cleardoublepage}
\listoffigures

\newpage{\thispagestyle{empty}\cleardoublepage}
\listoftables

@@

\newcommand{\vananh}{Huynh-Thu}%{V\^an Anh}

>>>>

\hypersetup{%
	pdftitle = {Modelling single cell dynamics with trajectories and gene regulatory networks},
	pdfsubject = {A subject},
	pdfkeywords = {import keywords},
	pdfauthor = {Robrecht Cannoodt},
	pdfcreator = {\LaTeX},
}

@@

	{\Huge \textsf{Modelling single cell dynamics\\with trajectories and gene regulatory networks}}

@@

%\newpage{\thispagestyle{empty}\cleardoublepage}
%\listoffigures

%\newpage{\thispagestyle{empty}\cleardoublepage}
%\listoftables

@@
